---
title: "ENVS-193DS_homework-03"
format: html
---

The link to my GitHub repository is [here](https://github.com/lperusa7/ENVS-193DS_homework-03)

## Setup

```{r}
warning = FALSE
message = FALSE

library(tidyverse)
library(here)
library(flextable)
library(readxl)
library(janitor)

# read in personal data
personal <- read_csv(
  # file path
  here("data", "ES193DS_Personal_Data.csv"))
```

# Problem 1: Personal Data

## a. 

For my personal data, I'm observing how many tasks I complete in a given study session, while listening to different genres of music during each study session to then be able to see if the music genre has an affect on my productivity rate. I then use the number of tasks completed to then calculate my productivity rate, to then compare the change in my productivity rate, which is (number of tasks / time), based on the different categories of music genres.

## b.


```{r, data-cleaning}
# creatig clean data frame
personal_cleaned <- personal |> # choosing personal data frame
  # cleaning column names
  clean_names() |>
  select(date, study_period, music_genre, work_environment, time_of_day, sleep, productivity)
```

```{r, making-plot}
ggplot(data = personal_cleaned,
       aes(x = music_genre,
           y = productivity)) +
  geom_boxplot(fill = "skyblue",
               color = "black") +
  geom_jitter(width = 0.2,
              alpha = 0.5,
              color = "darkblue") +
  geom_point() +
         labs(x = "Music Genre",
              y = "Productivity (Tasks completed per hour)",
              title = "Average Task Completion Rate Based on Music Genre") +
         theme_minimal()
```
